---
title: "drawing_covid"
author: "Mohammad Hamdan"
date: "1/28/2022"
output: pdf_document
---

```{r setup, include=FALSE}
library(drawingcovid)
library(tidyverse)
library(ambient)
library(scico)
library(here)
```

This incredible new function helps us to visualize the horrors of coronavirus (in an interpretative way, of course). simply enter any number: your phone number, BSN, birthday, the batch number from your vaccine and the algorithm will generate a nasty, slimy picture of what coronavirus may or may not look like! (not sure because i haven't actually googled it.

You need to install the following packages for it to work (if you haven't already):

```{r libraries, eval = FALSE}
install.packages("tidyverse")
install.packages("ambient")
install.packages("scico")
install.packages("here")
```

```{r random number 1}
make_art(27)
```

```{r date}
make_art(24012022) 
```

```{r backwards date}
make_art(22020124)
```

```{r another random number}
make_art(24348023) 
```

\newpage
If you can't think of a number then we got you covered:
```{r no number}
make_art() 
```
